### 2021-05-12 docs/manuscript/PLOS-MSc-Thesis.tex
Improve Fig2 caption

\begin{figure}[!h]
 \includegraphics[width=\textwidth]{figures/results/Fig2}
 \caption{\bf Distribution of abundances of network topologies.}
 Most frequent network topologies shown in the grid contain the I3-FFL network
 motif. Topologies are numbered in order of decreasing abundance. The number of
 GRNs belonging to each network topology is presented below topology number.
 Note that network topology number 9 produces the striped phenotype using a
 two-node GRN.
 \label{fig:distopol}
\end{figure}

>>>>

\begin{figure}[!h]
 \includegraphics[width=\textwidth]{figures/results/Fig2}
 \caption{\bf Distribution of abundances of network topologies.}
 \hil{Some of the most} frequent network topologies shown in the grid
 contain the I3-FFL network motif \hil{(shown on the left). In this network
 motif the gene B is activated in an indirect way by the morphogen through
 the activation of A (positive interactions), and at the same time, it
 is inactivated in a direct way by the morphogen (negative interaction).}
 Topologies are numbered in order of decreasing abundance, \hil{being the
 Topology 1 the most abundant with a number of 95 genotypes}. The number of
 \hil{genotypes} belonging to each network topology is presented below
 topology number.
 Note that network topology number 9 produces the striped phenotype using a
 two-node GRN.
 \label{fig:distopol}
\end{figure}
